---
title: "CRIM 595 Project Template"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

Here's a collection of text formatting/styling things you may (or may not) care about. Copy them, use them, or delete them, just don't leave all of this here when you submit your project...

There's a [useful link here](https://www.rforecology.com/post/how-to-use-rmarkdown-part-one/).

And here's [another one](https://sage-fenglisu-c38dfb.netlify.app/). 

[Here's a great link](https://bookdown.org/yihui/rmarkdown-cookbook/kable.html) for creating tables as visuals in your file.

Both of the examples above show you how to hyperlink text. That's useful when you want to cite something, without providing the URL in the text.

These are different heading styles. When you 'knit' this template, you see how they differ:

# Heading 1
## Heading 2
### Heading 3
#### Heading 4
##### Heading 5
###### Heading 6

### *Italics*
### **Bold**
### ***Bold Italicized**

1. Numbered
2. List
3. Like
4. This

* bullet points
- work
* like this
- or this

*When you are ready to see what the output looks like*, **click the 'Knit' button.** The output file will be saved to the same folder this script is saved to.

# Example Section
```{r, echo=FALSE, message=FALSE, results='hide'}
# when you set 'echo' to false, you are hiding the block of code 
# when you set 'message' to false, you are hiding the console text that comes after running your code
# when you set 'results' to hide, you are hiding extra processing that occasionally shows up in the console
```
See how the chunk of code above doesn't show up in the knitted output? It's magic, really.

# PACKAGES
```{r}
#install.packages('tidyverse')
library(tidyverse)
```
**NOTE:** *Never ever ever include any install.packages functions.* Either comment them out with a #, or delete them.

Also, if we had used the message=FALSE here, all that extra stuff would not have displayed in the knit.

# SOURCES
```{r}
# Data source link here 
```
A completely optional section for any data source references.

## Acquire Data
```{r}
# Code here
```
Often, this is the section where you include how you got the data.

## Wrangle Data
```{r}
# more code heree
```
This is typically where any processing, extracting, and/or formatting occurs.

## Calculate Data
```{r}
# more code
```
This can be the place where math is done. **Wrangle** and **Calculate** can often be one section, too.

## Visualize Data
```{r}
# yep, more code, but with graphs
```
A place for graphs, maps, etc.

# ANALYTICS
Insert text here for your actual findings and results. You can also insert text above/below visualizations along the way.

**NOTE:** When submitting your projects, you are submitting either an **HTML** or **PDF** output of your Markdown file. Blackboard does not accept HTML files, so if you go that route (*and I recommend it, really*), [email me](mailto:mdanna2@gmu.edu) a copy of your final submission.
